### 2020-01-30 wuhan.tex
More ambitious intro

We evaluate six disparate models posted online in daterange that estimated \Ro\ for the 2019-nCoV outbreak. <C-F3>
Our results indicate that most early estimates of $\mathcal R_0$ for the outbreak
are likely to have been overly confident.

>>>>

We evaluate six disparate models posted online between January 24--26, 2020 that estimated \Ro\ for the 2019-nCoV outbreak. We use our framework to construct pooled estimates for the underlying parameters. We use these pooled estimates to illustrate the importance of propagating different sources of error, particularly uncertainty in both the growth rate and the generation interval. We also use our framework to unravel which assumptions of these different models led to their different estimates and confidence intervals.

Our results indicate that many early estimates of \Ro\ were likely overly confident.
